---
title: "COVID19 Data Near Grace College"
author: "Compiled by Dr. Ryan Johnson using data from [@COVID19]"
output:
  html_document:
    df_print: paged
bibliography: bibliography.bib
---

```{r, echo=FALSE}
library(COVID19)
require(tidyverse)
library(dplyr)
library(lubridate)
library(scales)
```

```{r echo=FALSE}
#Input parameters
per = 10^4 #dislplay rates per how many people?
per_word = "Ten Thousand"
data_start = as.Date("2020-03-20") #Start data at this day
```

```{r echo=FALSE}
#Get data and subset to states we want
US_states <- covid19("US", level = 2, start = data_start)
states <- c("Indiana", "Michigan", "Illinois", "Ohio", "Kentucky")
neighbors <- subset(US_states, state %in% states)
```

```{r echo=FALSE}
#What is the latest date of the data?
yest <- max(US_states$date)
```

```{r echo=FALSE}
#Get per-day numbers
neighbors$difdeaths <- prepend(diff(neighbors$deaths), 0)
neighbors$difconfirmed <- prepend(diff(neighbors$confirmed), 0)
neighbors$diftests <- prepend(diff(neighbors$tests), 0)
```

```{r echo=FALSE}
#Get per-population numbers
neighbors$confirmedper <- neighbors$confirmed / neighbors$pop * per
neighbors$deathsper <- neighbors$deaths / neighbors$pop * per
neighbors$testsper <- neighbors$tests / neighbors$tests * per
neighbors$difconfirmed_per <- neighbors$difconfirmed / neighbors$pop * per
neighbors$difdeaths_per <- neighbors$difdeaths / neighbors$pop * per
neighbors$diftests_per <- neighbors$diftests / neighbors$pop * per
```

```{r echo=FALSE}
#Some convenient date subsets
covyest <- neighbors[neighbors$date == yest,]
covlabel <- neighbors[neighbors$date == as.Date("2020-04-20"),]
cov5 <- neighbors[neighbors$date <= yest & neighbors$date > (yest - 5),]
cov14 <- neighbors[neighbors$date <= yest & neighbors$date > (yest - 14),]
```

&nbsp;

# Data from Indiana and Neighboring States

&nbsp;

### Confirmed Deaths from COVID19

Deaths data are the best indicator of the real prevalence of the disease, but deaths data lags behind case data.

All numbers in this graph are per `r tolower(per_word)`.  Dots are the number of new deaths recorded each day.  Dashed lines are a weighted average.


```{r, echo=FALSE, fig.width = 12, fig.height = 16}
#Plot Deaths per Million per Day
ggplot(neighbors, aes(x = date, y = difdeaths_per, color = state)) + 
  geom_point(size = 4) +
  scale_x_date(date_labels="%b %d",
               date_breaks  ="3 days",
               minor_breaks = "1 day") + 
  scale_y_continuous(limit=c(0,NA), oob = squish) +
  ggtitle(paste("Deaths per Day per", per_word, "People")) + 
  theme(plot.title = element_text(hjust = 0.5), legend.text = element_text(size = 15)) + 
  ylab(paste("Deaths per Day per", per_word, "People")) + 
  xlab("Date") +
  stat_smooth(size = 1, se = FALSE, linetype = "dashed") +
  facet_wrap(vars(state), nrow = 3, ncol = 2)
```

### Confirmed Cases of COVID19

The case data below is also per `r tolower(per_word)`.  Dots are new confirmed cases of COVID19 each day.  The dashed lines are weighted averages.

```{r, echo=FALSE, fig.width=12, fig.height=8}
ggplot(neighbors, aes(x = date, y = difconfirmed_per, color = state)) + 
  geom_point(size = 4) +
  scale_x_date(date_labels="%b %d",
               date_breaks  ="3 days",
               minor_breaks = "1 day") + 
  scale_y_continuous(limit=c(0,NA), oob = squish) +
  ggtitle(paste("Confirmed Cases per Day per", per_word, "People")) + 
  theme(plot.title = element_text(hjust = 0.5), legend.text = element_text(size = 15)) + 
  ylab(paste("Cases per Day per", per_word, "People")) + 
  xlab("Date") +
  stat_smooth(size = 1, se = FALSE, linetype = "dashed")
```

### Positive Test Rate

Looking at the percentage of tests that come back positive can signal which states might have low case numbers because of lack of testing.

For example, Michigan had a much higher death rate per capita than Illinois in mid-April, even though their case numbers per capita were only a little higher in late March and early April.  Michigan's high postive test rate late March and early April suggests that Michigan had worse testing than Illinois during that time.

```{r, echo=FALSE, fig.width=12, fig.height=8}
ggplot(neighbors, aes(x = date, y = (difconfirmed / diftests), color = state)) + 
  geom_point(size = 4) +
  scale_x_date(date_labels="%b %d",
               date_breaks  ="3 days",
               minor_breaks = "1 day") + 
  scale_y_continuous(limit=c(0,1), oob = squish, labels = scales::percent) +
  ggtitle("Percent Tests Positive each Day (Smoothed Running Average)") + 
  theme(plot.title = element_text(hjust = 0.5), legend.text = element_text(size = 15)) + 
  ylab("Percent Tests Positive") + 
  xlab("Date") +
  stat_smooth(size = 1, se = FALSE, linetype = "dashed")
```
&nbsp;

# County Level Data

```{r echo=FALSE}
#Redo parameters
per = 10^4
per_word = "Ten Thousand"
```

```{r echo=FALSE}
#County Level Data
US_counties <- covid19("US", level = 3, start = data_start)
cn <- c("Kosciusko", "Fulton", "Marshall", "Saint Joseph", "Elkhart", "LaGrange", "Noble", "Whitley", "Allen", "Huntington", "Wabash", "Miami", "Cass")
IN_neighbors <- subset(US_counties, state == "Indiana" & city %in% cn)
IN_neighbors$county <- as.factor(IN_neighbors$city)
```

```{r echo=FALSE}
#Get per-day numbers
IN_neighbors$difdeaths <- prepend(diff(IN_neighbors$deaths), 0)
IN_neighbors$difconfirmed <- prepend(diff(IN_neighbors$confirmed), 0)
IN_neighbors$diftests <- prepend(diff(IN_neighbors$tests), 0)
```

&nbsp;

### Nearest Outbreak


```{r echo=FALSE}
#Get per-population numbers
IN_neighbors$confirmedper <- IN_neighbors$confirmed / IN_neighbors$pop * per
IN_neighbors$deathsper <- IN_neighbors$deaths / IN_neighbors$pop * per
IN_neighbors$testsper <- IN_neighbors$tests / IN_neighbors$tests * per
IN_neighbors$difconfirmed_per <- IN_neighbors$difconfirmed / IN_neighbors$pop * per
IN_neighbors$difdeaths_per <- IN_neighbors$difdeaths / IN_neighbors$pop * per
IN_neighbors$diftests_per <- IN_neighbors$diftests / IN_neighbors$pop * per
```

The nearest outbreak is in Cass County, Indiana.  It appears to be linked to the Tyson meatpacking plant.

```{r echo=FALSE}
outbreaks = c("Cass")
IN_outbreaks <- subset(IN_neighbors, county %in% outbreaks)
```

```{r echo=FALSE, fig.width=12, fig.height=8}
ggplot(IN_outbreaks, aes(x = date, y = difconfirmed_per * pop / per)) + 
  geom_point(size = 4) +
  scale_x_date(date_labels="%b %d",
               date_breaks  ="3 days",
               minor_breaks = "1 day") + 
#  scale_y_log10(breaks = breaks, minor_breaks = minor_breaks) + 
  scale_y_continuous(limit=c(0,NA), oob = squish) +
  ggtitle(paste("Total Confirmed Cases per Day.", outbreaks[[1]], "County population is", as.character(IN_outbreaks$pop[[1]]))) + 
  theme(plot.title = element_text(hjust = 0.5), legend.text = element_text(size = 15)) + 
  ylab(paste("Total Cases per Day")) + 
  xlab("Date")
```

&nbsp;

### Non-outbreak Neighbors

Besides Cass County, our neighboring counties have case levels that can fit in roughly the same scale.  Notice that the cases below are reported per `r tolower(per_word)` people.

```{r echo=FALSE}
IN_not_outbreaks <- subset(IN_neighbors, !(county %in% outbreaks))
```

```{r, echo=FALSE, fig.width=12, fig.height=20}
#Plot Confirmed per Million per Day
#breaks <- 10^(-10:10)
#minor_breaks <- rep(1:9, 21)*(10^rep(-10:10, each=9))
ggplot(IN_not_outbreaks, aes(x = date, y = difconfirmed_per, color = county)) + 
  geom_point(size = 4) +
  scale_x_date(date_labels="%b %d",
               date_breaks  ="3 days",
               minor_breaks = "1 day") + 
#  scale_y_log10(breaks = breaks, minor_breaks = minor_breaks) + 
  scale_y_continuous(limit=c(0,NA), oob = squish) +
  ggtitle(paste("Confirmed Cases per Day per", per_word, "People")) + 
  theme(plot.title = element_text(hjust = 0.5), legend.text = element_text(size = 15)) + 
  ylab(paste("Cases per Day per", per_word, "People")) + 
  xlab("Date") +
  facet_wrap(vars(county), nrow = 6, ncol = 2)
```


